Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-06-09 docs/00-manuscripts/ieee/ieee-manuscript.tex
clarify pairwise cor feature removal

Individual features were finally removed from these feature sets if they were numerically equivalent to another feature based on their pairwise correlation being greater than $1 - 10^{-10}$.
This preprocessing step reduced the number of covariates to 122 (HR), 86 (VI) and 7467 (NRI).

>>>>

Some individual features were finally removed from these feature sets if they were numerically equivalent to another feature based on their pairwise correlation being greater than $1 - 10^{-10}$.
This preprocessing step reduced the number of covariates to 122 (HR), 86 (VI) and 7467 (NRI).
